Modular Curves

### 2020-01-28 paper.tex
fixed typos

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage[dutch]{babel}
\usepackage{amsmath, amssymb, amsthm}
%\usepackage{geometry}
\usepackage{tikz-cd}
\usepackage{mdframed}
\usepackage{color}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{todonotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}
% figure support
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
	\def\svgwidth{\columnwidth}
	\import{./figures/}{#1.pdf_tex}
}

@@

\newtheoremstyle{theoremdd}% name of the style to be used
  {7pt}% measure of space to leave above the theorem. E.g.: 3pt
  {7pt}% measure of space to leave below the theorem. E.g.: 3pt
  {\itshape}% name of font to use in the body of the theorem
  {0pt}% measure of space to indent
  {\bfseries}% name of head font
  {}% punctuation between head and body
  { }% space after theorem head; " " = normal interword spae
  {\thmname{#1}\thmnumber{ #2}\thmnote{ (#3)}}

\newtheoremstyle{definitiondd}% name of the style to be used
  {7pt}% measure of space to leave above the theorem. E.g.: 3pt
  {7pt}% measure of space to leave below the theorem. E.g.: 3pt
  {\rmfamily}% name of font to use in the body of the theorem
  {0pt}% measure of space to indenlt
  {\bfseries}% name of head font
  {}% punctuation between head and body
  { }% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2}\thmnote{ (#3)}}

  \newtheoremstyle{remarkdd}% name of the style to be used
  {7pt}% measure of space to leave above the theorem. E.g.: 3pt
  {7pt}% measure of space to leave below the theorem. E.g.: 3pt
  {\rmfamily}% name of font to use in the body of the theorem
  {0pt}% measure of space to indent
  {\itshape}% name of head font
  {}% punctuation between head and body
  { }% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2} \thmnote{ (#3)}}

@@

Elliptic curves are related to complex tori, by the meromorphic functions from the complex tori to the complex plane. These functions are also called \emph{elliptic functions}. 
A elliptic function $\phi: \C / \Lambda \to \C \cup \{\infty\} $ is naturally identified with a  $\Lambda$-periodic function $\phi': \C \to \C \cup \{\infty\}: z \mapsto \phi(z + \Lambda)$. 
We will often make use of this identification implicitly. 
One may wonder how a non-trivial example of such a function looks like. 
One example of particular interest is the \emph{Weierstrass $\wp$-function}. 
For a given lattice  $\Lambda$ we define this function to be \[
	\wp(z) = \frac{1}{z^2} + \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0}}\left( \frac{1}{(z-\omega)^2} - \frac{1}{\omega^2} \right) 
.\] 
At first glance it seems obvious that such a function is $\Lambda$ periodic, but we have to be careful. 
While this sum is absolutely convergent on compact sets, its is not if we split up $\frac{1}{(z-\omega^2)} - \frac{1}{\omega^2}$ into two different summations. So we cannot simply permute the terms in the desired way. 
It still is $\Lambda$-periodic. Indeed, notice that  \[
	\wp'(z) = -2 \sum_{\omega \in \Lambda} \frac{1}{(z - \omega)^3}
\] 
this is periodic function as we can permute the terms in the sum.
We will now show that this implies that $\wp$ is $\Lambda$-periodic (exercise 1.4.2).
Note that $\wp$ is symmetric, as showing this can indeed be achieved by permuting the right terms.
For any $\omega \in \Lambda$ is holds that 
\[
	(\wp(z) - \wp(z + \omega))' = \wp'(z) - \wp'(z+ \omega) = 0 
.\] 
From this it follows that $\wp(z) - \wp(z + \omega)$ is constant a constant function of $z$, everywhere where it is defined.
In particular it is the case that \[
	\wp\left(-\frac{\omega}{2}\right) - \wp\left(\omega - \frac{\omega}{2}\right) = \wp\left(\frac{\omega}{2}\right) - \wp\left(\frac{\omega}{2}\right)  = 0 
.\] 
So $\wp(z) = \wp(z+ \omega)$. 
We conclude that $\wp$ is $\Lambda$-periodic.

@@

Recall that \emph{Eisenstein-series} $G_k$ is the function defined as \[
	G_k(\tau) = \sum_{\substack{c, d \in \Z^2 \\ (c, d) \ne 0}} \frac{1}{(c\tau + d)^{k}}
.\] 
Note that this is equal to \[
	G_k(\tau) = \sum_{\substack{\omega \in \Lambda_\tau \\ \omega \ne 0}} \frac{1}{\omega}
.\] 
In this spirit we extend the definition of the eisentein series as follows. For a given lattice $\Lambda$ and an even number  $k > 2$ we define \[
	G_k(\Lambda) = \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0}} \frac{1}{\omega^{k}}
.\] 
This is indeed a very natural generalisation as $G_k(\tau) = G_k(\Lambda_\tau)$.

We can describe the Laurent expansion of $\wp$ using these Eisenstein series.
\begin{proposition}\label{prop:laurent_weierstrass}
  Let $\Lambda$ be a lattice. Then the Laurent expansion of $\wp_\Lambda$ is \[
	  \wp_\Lambda(z) = \frac{1}{z^2} \sum_{\substack{n = 2 \\ n \text{ even}}}^{\infty}(n+ 1) G_{n + 2}(\Lambda)z^{n}
  .\] 
\end{proposition}
\begin{proof}
	As we are dealing with analytical functions it is sufficient to show equality on an non empty open. We choose a neighbourhood of 0 such that in that neighbourhood $|z| < |\omega|$ for all $\omega \in \Lambda \setminus \{ 0\} $. It that case it holds that. 
\begin{align*}
	\frac{1}{(z- \omega)^2} - \frac{1}{\omega^2} &= \frac{1}{\omega^2}\left( \left( \frac{1}{(1-z / \omega)} \right) ^2 - 1 \right)  \\
						     &= \frac{1}{\omega^2}\left( \left( \sum_{n = 0}^{\infty} \left(\frac{z}{\omega}\right)^{n} \right)^2 - 1  \right) \\
						     &= \frac{1}{\omega^2}\left( \sum_{n = 0}^{\infty} (n + 1)  \left( \frac{z}{\omega} \right) ^{n} - \right)  \\
						     &= \sum_{n = 1}^{\infty} (n + 1)  \frac{z^{n}}{\omega^{n+2}} \\
\end{align*}	
We can fill this in in the expression for $\wp_\Lambda$ yields
\begin{align*}
	\wp(z) &= 
	\frac{1}{z^2} + \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0 }} \frac{1}{(z - \omega)^2} - \frac{1}{\omega^2} \\
	       &=  \frac{1}{z^2} + \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0}} \sum _{n = 1}^{\infty} (n + 1)  \frac{z^{n}}{\omega^{n+2}}\\
	       &= \frac{1}{z^2} + \sum_{n = 1}^{\infty}\sum_{\substack{\omega \in \Lambda \\ \omega \ne 0 }} (n + 1) \frac{z^{n}}{\omega^{n+2}} \\
\end{align*}
We can exchange the order of summation as it turns out that this is an absolutely convergent series. 
When $n$ is odd we see that every term $ (n + 1) \frac{z^{n}}{\omega^{n+2}}$ cancels against $(n + 1) \frac{z^{n}}{(-\omega)^{n+2}}$. 
So we find that 
\begin{align*}
	\wp(z) &= \frac{1}{z^2} + \sum_{\substack{n = 2\\ n \text{ even}}}^{\infty}\sum_{\substack{\omega \in \Lambda \\ \omega \ne 0 }} (n + 1) \frac{z^{n}}{\omega^{n+2}} \\
	       &=\frac{1}{z^2} + \sum_{\substack{n = 2 \\ n \text{ even}}}^{\infty} (n+1) G_{n + 2}(\Lambda) z^{n}
.\end{align*}
\end{proof}
The function $\wp$ what connects complex tori to elliptic curves. 
\begin{theorem}\label{thm:complex_tori_elliptic_curves}
	Let $\Lambda = \omega_1 \oplus \omega_2$ be a lattice. Then for every $z + \Lambda$, the function  $(\wp_\Lambda(z), \wp'_\Lambda(z))$ is a point on the following cubic equation \begin{equation} \label{eq:cubic_curve_lattice}
		y^2 = 4x^3 - g_2(\Lambda)x - g_{3}(\Lambda)
	,\end{equation}
	where $g_2(\Lambda) = 60 G_4(\Lambda), g_3(\Lambda) = 140 G_6(\Lambda)$.
	The right hand side of this equation also factors in the following way \[
		y^2 = 4x^3 - g_2(\Lambda) x^2 - g_3(\Lambda) = 4\left(x - \wp_\Lambda\left(\frac{\omega_1}{2}\right)\right)\left(x - \wp_{\Lambda}\left(\frac{\omega_2}{2}\right)\right)\left(x - \wp\left(\frac{\omega_1 + \omega_2}{2}\right)\right)
	.\] 
\end{theorem}
\begin{proof}
	To prove \cref{eq:cubic_curve_lattice} we will first show that the equality holds for the first few terms of the Laurent expansion and then use a little trick using the periodicity of $\wp_\Lambda$ and $\wp'_\Lambda$.
	We know that (\cref{prop:laurent_weierstrass})\[
		\wp_\Lambda(z) = \frac{1}{z^2} + 3 G_4(\Lambda) z^2 + 5G_6(\Lambda) z^{4} + \mathcal{O} (z^{6})
	.\] 
	Similarly we see that \[
		\wp'_\Lambda = - \frac{2}{z^3} + 6 G_4(\Lambda)z + 20G_6(\Lambda)z^3 + \mathcal{O} (z^{5})	
	.\] 
	Using these expansions one can easily verify that \[
		(\wp'_\Lambda(z))^2 - 4(\wp(z))^3 + g_2(\Lambda)\wp_{\lambda}(z) + g_{3}(\Lambda)    = \mathcal{O} (z^{2})
	.\] 
	This expression is holomorphic and $\Lambda$-periodic. So it's bounded. We know that it must be zero as it is zero when  $z \to 0$. 
	As a result we find \cref{eq:cubic_curve_lattice}.

@@

Let's try to unpack the statement of \cref{thm:complex_tori_elliptic_curves}.
The first part shows that there is a map from a comples torus to an elliptic curve 
\begin{align*}
	\frac{\C}{\Lambda} &\longrightarrow \text{elliptic curve: } Z(x^3 - a x - b -y ^2) \\
	z+\Lambda &\longmapsto \left(\wp_\Lambda(z), \wp'_\Lambda(z)\right)
.\end{align*}
We know that this is an elliptic curve as it the right hand side has three distinct roots so its determinant $a^2 - 27 b^3 \ne 0  $.
We can see that this map is bijective. By \cref{ex:1.4.1}  $\wp_\Lambda$  takes every value twice. As this is an even function a certain $x \in \C$ must be taken twice, once by $z$ once by $-z$ and because $\wp'$ is an odd function $\wp'(z) \ne \wp'(-z)$ unless $z = 0$.  By for every $x$-value there are exactly two $y$ values on the elliptic curve. So this is indeed a bijection.

We will now show that this map is in fact a group isomorphism.
Let $z_1 + \Lambda, z_2 + \Lambda$ be points in $\C / \Lambda$.
These correspond to two points $P = (\wp_{\Lambda}(z_1), \wp'_\Lambda(z_1))$ and $ Q = (\wp_{\Lambda}(z_2), \wp'_\Lambda(z_2))$ in $\C^2$. 
Let $ax + by + c = 0$ be the line that intersects the elliptic curve in both these points (with intersection number 2 if  $z_1 = z_2$).
Define the function \[
	f(z) = a \wp_{\Lambda}(z) + b \wp'_\Lambda(z) + c
.\] 
Clearly $z_1, z_2$ are two zeros of this function. Obviously the third interesction of the line with the curve corresponds to the third zero of $f$. 
By \cref{ex:1.4.1} we see that this third zero $z_3$ must be such that $z_1 + z_2 + z_3 + \Lambda = 0 + \Lambda$. 
Hence $z_3 = - z_1 - z_2$. Its corresponding point on the elliptic curve is 
$(\wp_\Lambda(z_3), \wp'_\Lambda(z_3)$. Then so $P + Q = (\wp_\Lambda(z_3), - \wp'_\Lambda(z_3)) = (\wp_\Lambda(-z_3), \wp'_\Lambda(-z_3)$. 
So the map respects the group action.

From now on we will often say complex elliptic curve, instead of complex torus to highlight their interpretation as elliptic curves. Further, we will often denote complex elliptic curves with a simple symbold (often $E$) instead of always writing them as the quotient  $\C / \Lambda$. We write $E_\tau  = \C / \Lambda_\tau$.

\todo{Optionally write about maps between complex curves}.

\section{Modular Curves and Moduli Spaces} \label{sec:modular_curves_and_moduli_spaces}
The title of this paper is modular curves, but so far have not defined these. 
The definition of these objects is very simple, but like any object in this paper, the real suprises are it's relations to other objects. 
\begin{definition}
	Let $\Gamma \subset \SL_2\Z$ be any congruence subgroup. Then the \emph{modular curve} $Y(\Gamma)$ is defined as the set of orbits of $\mathcal{H} $ under  $\Gamma$, \[
		Y(\Gamma) = \mathcal{H} / \sim = \{\Gamma \tau \;|\; \tau \in \mathcal{H} \} 
	.\] 
\end{definition}
Recall the subgroups $\Gamma(N), \Gamma_1(N), \Gamma_0(N)$ from \cref{sec:subgroups_of_the_modular_group}. 
Often we are interested in the modular curves corresponding to these congruence subgroups, so we denote \[
	Y_0(N) = Y(\Gamma(N)),\; Y_1(N) = Y(\Gamma_1(N)),\; Y(N) = Y(\Gamma(N))
.\]

In \cref{sec:modular_forms_and_complex_tori} we have seen that there is a bijective correspondence between equivaleny classes of complex elliptic curves and points in $Y (\SL_2\Z)$. 
One may wonder whether there there is a similar result for modular curves $Y_0(N)$ and $Y_1(N)$.
It turns out there is. 
Instead of restricting the isomorphisms between the complex elliptic curves, we will actually give the elliptic curves extra information, resulting in \emph{enhanced elliptic curves}.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
%\usepackage[dutch]{babel}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{tikz-cd}
\usepackage{mdframed}
\usepackage{color}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{todonotes}
\usepackage[backend=biber]{biblatex}
\addbibresource{references.bib}
% figure support
\usepackage{import}
\usepackage{xifthen}
\usepackage{pdfpages}
\usepackage{transparent}
\newcommand{\incfig}[1]{%
	\def\svgwidth{\columnwidth}
	\import{./figures/}{#1.pdf_tex}
}

@@

\newtheoremstyle{theoremdd}% name of the style to be used
  {7pt}% measure of space to leave above the theorem. E.g.: 3pt
  {7pt}% measure of space to leave below the theorem. E.g.: 3pt
  {\itshape}% name of font to use in the body of the theorem
  {0pt}% measure of space to indent
  {\bfseries}% name of head font
  {}% punctuation between head and body
  { }% space after theorem head; " " = normal interword spae
  {\thmname{#1}\thmnumber{ #2}\thmnote{ (#3) } \hspace{.1cm}}

\newtheoremstyle{definitiondd}% name of the style to be used
  {7pt}% measure of space to leave above the theorem. E.g.: 3pt
  {7pt}% measure of space to leave below the theorem. E.g.: 3pt
  {\rmfamily}% name of font to use in the body of the theorem
  {0pt}% measure of space to indenlt
  {\bfseries}% name of head font
  {}% punctuation between head and body
  { }% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2}\thmnote{ (#3) } \hspace{.1cm}}

  \newtheoremstyle{remarkdd}% name of the style to be used
  {7pt}% measure of space to leave above the theorem. E.g.: 3pt
  {7pt}% measure of space to leave below the theorem. E.g.: 3pt
  {\rmfamily}% name of font to use in the body of the theorem
  {0pt}% measure of space to indent
  {\itshape}% name of head font
  {}% punctuation between head and body
  { }% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2} \thmnote{ (#3)} \hspace{.1cm}}

@@

Elliptic curves are related to complex tori, by the meromorphic functions from the complex tori to the complex plane. These functions are also called \emph{elliptic functions}. 
A elliptic function $\phi: \C / \Lambda \to \C \cup \{\infty\} $ is naturally identified with a  $\Lambda$-periodic function $\phi': \C \to \C \cup \{\infty\}: z \mapsto \phi(z + \Lambda)$. 
We will often make use of this identification implicitly. 
One may wonder how a non-trivial example of such a function looks like. 
One example of particular interest is the \emph{Weierstrass $\wp$-function}. 
For a given lattice  $\Lambda$ we define this function to be \[
	\wp(z) = \frac{1}{z^2} + \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0}}\left( \frac{1}{(z-\omega)^2} - \frac{1}{\omega^2} \right) 
.\] 
At first glance it seems obvious that such a function is $\Lambda$ periodic, but we have to be careful. 
While this sum is absolutely convergent on compact sets, its is not if we split up $\frac{1}{(z-\omega^2)} - \frac{1}{\omega^2}$ into two different summations. So we cannot simply permute the terms in the desired way. 
It still is $\Lambda$-periodic. Indeed, notice that  \[
	\wp'(z) = -2 \sum_{\omega \in \Lambda} \frac{1}{(z - \omega)^3}
\] 
this is periodic function as we can permute the terms in the sum.
We will now show that this implies that $\wp$ is $\Lambda$-periodic (exercise 1.4.2).
Note that $\wp$ is symmetric, as in this case we can permute the right terms.
For any $\omega \in \Lambda$ is holds that 
\[
	(\wp(z) - \wp(z + \omega))' = \wp'(z) - \wp'(z+ \omega) = 0 
.\] 
From this it follows that $\wp(z) - \wp(z + \omega)$ is a constant function of $z$, everywhere where it is defined.
In particular it is the case that \[
	\wp\left(-\frac{\omega}{2}\right) - \wp\left(\omega - \frac{\omega}{2}\right) = \wp\left(\frac{\omega}{2}\right) - \wp\left(\frac{\omega}{2}\right)  = 0 
.\] 
So $\wp(z) = \wp(z+ \omega)$. 
We conclude that $\wp$ is $\Lambda$-periodic.

@@

Recall that \emph{Eisenstein-series} $G_k$ is the function defined as \[
	G_k(\tau) = \sum_{\substack{c, d \in \Z^2 \\ (c, d) \ne 0}} \frac{1}{(c\tau + d)^{k}}
.\] 
Note that this is equal to \[
	G_k(\tau) = \sum_{\substack{\omega \in \Lambda_\tau \\ \omega \ne 0}} \frac{1}{\omega}
.\] 
In this spirit we extend the definition of the Eisenstein series as follows. For a given lattice $\Lambda$ and an even number  $k > 2$ we define \[
	G_k(\Lambda) = \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0}} \frac{1}{\omega^{k}}
.\] 
This is indeed a very natural generalisation as $G_k(\tau) = G_k(\Lambda_\tau)$.

We can describe the Laurent expansion of $\wp$ using these Eisenstein series.
\begin{proposition}\label{prop:laurent_weierstrass}
  Let $\Lambda$ be a lattice. Then the Laurent expansion of $\wp_\Lambda$ is \[
	  \wp_\Lambda(z) = \frac{1}{z^2} \sum_{\substack{n = 2 \\ n \text{ even}}}^{\infty}(n+ 1) G_{n + 2}(\Lambda)z^{n}
  .\] 
\end{proposition}
\begin{proof}
	As we are dealing with analytical functions it is sufficient to show equality on an non-empty open. We choose a neighbourhood of 0 such that in that for every $z$ in that neighbourhood $|z| < |\omega|$ for all $\omega \in \Lambda \setminus \{ 0\} $. It that case the following calculation is valid. 
\begin{align*}
	\frac{1}{(z- \omega)^2} - \frac{1}{\omega^2} &= \frac{1}{\omega^2}\left( \left( \frac{1}{(1-z / \omega)} \right) ^2 - 1 \right)  \\
						     &= \frac{1}{\omega^2}\left( \left( \sum_{n = 0}^{\infty} \left(\frac{z}{\omega}\right)^{n} \right)^2 - 1  \right) \\
						     &= \frac{1}{\omega^2}\left( \sum_{n = 0}^{\infty} (n + 1)  \left( \frac{z}{\omega} \right) ^{n} - \right)  \\
						     &= \sum_{n = 1}^{\infty} (n + 1)  \frac{z^{n}}{\omega^{n+2}} \\
\end{align*}	
Putting this result in the expression for $\wp_\Lambda$ yields
\begin{align*}
	\wp(z) &= 
	\frac{1}{z^2} + \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0 }} \frac{1}{(z - \omega)^2} - \frac{1}{\omega^2} \\
	       &=  \frac{1}{z^2} + \sum_{\substack{\omega \in \Lambda \\ \omega \ne 0}} \sum _{n = 1}^{\infty} (n + 1)  \frac{z^{n}}{\omega^{n+2}}\\
	       &= \frac{1}{z^2} + \sum_{n = 1}^{\infty}\sum_{\substack{\omega \in \Lambda \\ \omega \ne 0 }} (n + 1) \frac{z^{n}}{\omega^{n+2}} \\
\end{align*}
We can exchange the order of summation as it turns out that this is an absolutely convergent series. 
When $n$ is odd we see that every term $ (n + 1) \frac{z^{n}}{\omega^{n+2}}$ cancels against $(n + 1) \frac{z^{n}}{(-\omega)^{n+2}}$. 
So we find that 
\begin{align*}
	\wp(z) &= \frac{1}{z^2} + \sum_{\substack{n = 2\\ n \text{ even}}}^{\infty}\sum_{\substack{\omega \in \Lambda \\ \omega \ne 0 }} (n + 1) \frac{z^{n}}{\omega^{n+2}} \\
	       &=\frac{1}{z^2} + \sum_{\substack{n = 2 \\ n \text{ even}}}^{\infty} (n+1) G_{n + 2}(\Lambda) z^{n}
.\end{align*}
\end{proof}
The function $\wp$ what connects complex tori to elliptic curves. 
\begin{theorem}\label{thm:complex_tori_elliptic_curves}
	Let $\Lambda = \omega_1 \oplus \omega_2$ be a lattice. Then for every $z + \Lambda$, the function  $(\wp_\Lambda(z), \wp'_\Lambda(z))$ is a point on the following cubic equation \begin{equation} \label{eq:cubic_curve_lattice}
		y^2 = 4x^3 - g_2(\Lambda)x - g_{3}(\Lambda)
	,\end{equation}
	where $g_2(\Lambda) = 60 G_4(\Lambda), g_3(\Lambda) = 140 G_6(\Lambda)$.
	The right hand side of this equation also factors in the following way \[
		4x^3 - g_2(\Lambda) x^2 - g_3(\Lambda) = 4\left(x - \wp_\Lambda\left(\frac{\omega_1}{2}\right)\right)\left(x - \wp_{\Lambda}\left(\frac{\omega_2}{2}\right)\right)\left(x - \wp\left(\frac{\omega_1 + \omega_2}{2}\right)\right)
	.\] 
\end{theorem}
\begin{proof}
	To prove \cref{eq:cubic_curve_lattice} we will first show that the equality holds for the first few terms of the Laurent expansion and then use a little trick using the periodicity of $\wp_\Lambda$ and $\wp'_\Lambda$.
	We know that (\cref{prop:laurent_weierstrass})\[
		\wp_\Lambda(z) = \frac{1}{z^2} + 3 G_4(\Lambda) z^2 + 5G_6(\Lambda) z^{4} + \mathcal{O} (z^{6})
	.\] 
	Similarly we see that \[
		\wp'_\Lambda = - \frac{2}{z^3} + 6 G_4(\Lambda)z + 20G_6(\Lambda)z^3 + \mathcal{O} (z^{5})	
	.\] 
	Using these expansions one can easily verify that \[
		(\wp'_\Lambda(z))^2 - 4(\wp(z))^3 + g_2(\Lambda)\wp_{\lambda}(z) + g_{3}(\Lambda)    = \mathcal{O} (z^{2})
	.\] 
	This expression is holomorphic and $\Lambda$-periodic. So it's bounded. We know that it must be zero as it is zero when  $z \to 0$. 
	As a result we find \cref{eq:cubic_curve_lattice}.

@@

Let's try to unpack the statement of \cref{thm:complex_tori_elliptic_curves}.
The first part shows that there is a map from a comples torus to an elliptic curve 
\begin{align*}
	\frac{\C}{\Lambda} &\longrightarrow \text{elliptic curve: } Z(x^3 - a x - b -y ^2) \\
	z+\Lambda &\longmapsto \left(\wp_\Lambda(z), \wp'_\Lambda(z)\right)
.\end{align*}
We know that this is an elliptic curve as it the right hand side has three distinct roots so its determinant $a^2 - 27 b^3 \ne 0  $.
We can see that this map is bijective. By \cref{ex:1.4.1}  $\wp_\Lambda$  takes every value twice. As this is an even function a certain $x \in \C$ must be taken twice, once by $z$ once by $-z$ and because $\wp'$ is an odd function $\wp'(z) \ne \wp'(-z)$ unless $z = 0$.  For every $x$-value there are exactly two $y$ values on the elliptic curve. So this is indeed a bijection.

We will now show that this map is in fact a group isomorphism.
Let $z_1 + \Lambda, z_2 + \Lambda$ be points in $\C / \Lambda$.
These correspond to two points $P = (\wp_{\Lambda}(z_1), \wp'_\Lambda(z_1))$ and $ Q = (\wp_{\Lambda}(z_2), \wp'_\Lambda(z_2))$ in $\C^2$. 
Let $ax + by + c = 0$ be the line that intersects the elliptic curve in both these points (with intersection number 2 if  $z_1 = z_2$).
Define the function \[
	f(z) = a \wp_{\Lambda}(z) + b \wp'_\Lambda(z) + c
.\] 
Clearly $z_1, z_2$ are two zeros of this function. Obviously the third interesction of the line with the curve corresponds to the third zero of $f$. 
By \cref{ex:1.4.1} we see that this third zero, $z_3$, must be such that $z_1 + z_2 + z_3 + \Lambda = 0 + \Lambda$. 
Hence $z_3 = - z_1 - z_2$. Its corresponding point on the elliptic curve is 
$(\wp_\Lambda(z_3), \wp'_\Lambda(z_3))$.
So $P + Q = (\wp_\Lambda(z_3), - \wp'_\Lambda(z_3)) = (\wp_\Lambda(-z_3), \wp'_\Lambda(-z_3)$. 
Thus the map respects the group action.

From now on we will often say complex elliptic curve, instead of complex torus to highlight their interpretation as elliptic curves. Further, we will often denote complex elliptic curves with a simple symbol (often $E$) instead of always writing them as the quotient  $\C / \Lambda$. In particular we write $E_\tau  = \C / \Lambda_\tau$.

I will state, but not prove, that the map from complex elliptic curves to ordinary elliptic curves is actually functorial, meaning that every morphism between complex elliptic curves corresponds to a morphism as a variety on the corresponding ordinary curves.

\section{Modular Curves and Moduli Spaces} \label{sec:modular_curves_and_moduli_spaces}
The title of this paper is modular curves, but so far have not defined these. 
The definition of these objects is very simple, but like any object in this paper, the real suprises are it's relations to other objects. 
\begin{definition}
	Let $\Gamma \subset \SL_2\Z$ be any congruence subgroup. Then the \emph{modular curve}, $Y(\Gamma)$, is defined as the set of orbits of elements in  $\mathcal{H} $ under  the action of $\Gamma$, \[
		Y(\Gamma) = \mathcal{H} / \sim = \{\Gamma \tau \;|\; \tau \in \mathcal{H} \} 
	.\] 
\end{definition}
Recall the subgroups $\Gamma(N), \Gamma_1(N), \Gamma_0(N)$ from \cref{sec:subgroups_of_the_modular_group}. 
Often we are interested in the modular curves corresponding to these congruence subgroups, so we denote \[
	Y_0(N) = Y(\Gamma_0(N)),\;\;\; Y_1(N) = Y(\Gamma_1(N)),\;\;\; Y(N) = Y(\Gamma(N))
.\]

In \cref{sec:modular_forms_and_complex_tori} we have seen that there is a bijective correspondence between equivaleny classes of complex elliptic curves and points in $Y (\SL_2\Z)$. 
One may wonder whether there there is a similar result for modular curves $Y_0(N),Y_1(N)$ and $Y(N)$.
It turns out there is. 
Instead of restricting the isomorphisms between the complex elliptic curves, we will actually give the elliptic curves extra information, resulting in \emph{enhanced elliptic curves}.

\subsection{Enhanced Elliptic Curves and Moduli Spaces} \label{sec:enhanced_elliptic_curves_and_moduli_spaces}
There are three common ways of `adding information' to elliptic curves, creating \emph{enhanced elliptic curves}. Moduli Spaces are equivalence classes of enhanced elliptic curves.  
\begin{definition} \hspace{\linewidth}
	\begin{enumerate}
		\item An \emph{enhanced elliptic curve for $\Gamma_0(N)$} is an pair $(E, C)$ where  $E$ is a complex elliptic curve and $C$ is an cyclic subgroup of order $N$.
		Two of these curves $(E_1, C_1), (E_2, C_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that restricts to an isomorphism from $C_1$ to $C_2$.
		The associated \emph{moduli space} is \[
			S_0(N) = \{ \text{enhanced elliptic curves for } \Gamma_0(N)\} / \sim
		.\] 
	\item An \emph{enhanced elliptic curve for $\Gamma_1(N)$} is an pair $(E, Q)$ where  $E$ is a complex elliptic curve and $Q$ is point in $E$ of order $N$.
		Two of these curves $(E_1, Q_1), (E_2, Q_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that maps $Q_1$ to $Q_2$.
		The associated \emph{moduli space} is \[
			S_1(N) = \{ \text{enhanced elliptic curves for } \Gamma_1(N)\} / \sim
		.\] 
	\item An \emph{enhanced elliptic curve for $\Gamma(N)$} is an tripple $(E, P, Q)$ where  $E$ is a complex elliptic curve and $P, Q$ are points in the $N$-torsion subgroup $E[N]$ such  that the weil pairing  $e_N(P, Q) = 1$.
		Two of these curves $(E_1, P_1, Q_1), (E_2, P_2, Q_2)$ are equivalent if and only if there is an isomorphism from $E_1$ to $E_2$ that maps $P_1$ to $P_2$ and $Q_1$ to $Q_2$
		The associated \emph{moduli space} is \[
			S(N) = \{ \text{enhanced elliptic curves for } \Gamma(N)\} / \sim
		.\] 
	\end{enumerate}	
\end{definition}
\begin{figure}[h]
	\centering
	\incfig{enhanced_elliptic_curves}
	\caption{Enhanced elliptic curves}
	\label{fig:enhanced_elliptic_curves}
\end{figure}
\Cref{fig:enhanced_elliptic_curves} gives a visualisation of these enhanced elliptic curves.
The following theorem gives a generalisation of the conclusion of \cref{sec:modular_forms_and_complex_tori}, showing that there are bijections in the modular curves $Y_0(N), Y_1(N), Y(N)$ and the moduli spaces $S_0(N), S_1(N), S(N)$, as well as providing more insight in what the moduli spaces look like. 
\begin{theorem}\label{thm:correspondence_modulispaces}
	\hspace{\linewidth}
	\begin{enumerate}
		\item Every enhanced elliptic curve for $\Gamma_0(N)$ is equivalent to curve of the form $(E_\tau, \left<1 / N + \Lambda_\tau \right>)$ for some $\tau \in \mathcal{H} $. 
			Two curves in this form $(E_\tau, \left<1 / N + \Lambda_\tau \right>)$ and $(E_\sigma, \left<1 / N + \Lambda_\sigma \right>)$ are equivalent if and only if $\Gamma_0\left( N \right) \tau = \Gamma_0(N) \sigma$. There is a bijective correspondence
			\begin{align*}
				S_0(N) &\longrightarrow Y_0(N) \\
				\left[\frac{\C}{\Lambda_\tau}, \left<\frac{1}{N} + \Lambda_\tau \right>\right] &\longmapsto \Gamma_0(\N)\tau
			.\end{align*}
